hoard
=====

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/ropensci/hoard.svg?branch=master)](https://travis-ci.org/ropensci/hoard)

`hoard` - manage cached files

Exposes a single `R6` object so that when the package is imported in another
package for managing cached files, you don't need to polute the NAMESPACE 
with a bunch of functions. (you can always just `hoard::fxn`, but 
with a single object there are other benefits as well [maintaining state, e.g.]).

## install

```{r eval=FALSE}
devtools::install_github("ropensci/hoard")
```

```{r}
library(hoard)
```

## usage

initialize client

```{r}
(x <- hoard::hord())
```

set cache path

```{r}
x$cache_path_set("foobar")
```

make the directory if doesn't exist

```{r}
x$mkdir()
```

put a file in the cache

```{r}
cat("hello world", file = file.path(x$cache_path_get(), "foo.txt"))
```

list the files

```{r}
x$list()
```

details

```{r}
x$details()
```

delete by file name

```{r}
x$delete("foo.txt")
x$list()
```

## todo

see [issue 1](https://github.com/ropensci/hoard/issues/1)

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/hoard/issues).
* License: MIT
* Get citation information for `hoard` in R doing `citation(package = 'hoard')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
