---
title: "Introduction to the hoardr package"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction to the hoardr package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

hoardr introduction
===================

`hoardr` is a package for managing cached files.

The benefit of using `hoardr` vs. raw `rapddirs` is that `hoardr` exposes
an easy to use `R6` class that has variables and functions within it, 
so you don't have to import function foo or bar, etc. Just a single 
object.

You can easily wrap `hoardr` with user facing functions in your own 
package to manage cached files.

If you find any bugs or have any feature requests get in touch at 
<https://github.com/ropensci/hoardr>.

## Install

Stable from CRAN

```{r eval=FALSE}
install.packages("hoardr")
```

Dev version

```{r eval=FALSE}
devtools::install_github(c("ropensci/hoardr"))
```

```{r}
library("hoardr")
```

## initialize client

```{r}
(x <- hoardr::hoard())
```

## set cache path

```{r}
x$cache_path_set("foobar")
```

## make the directory if doesn't exist

```{r}
x$mkdir()
```

## put a file in the cache

```{r}
cat("hello world", file = file.path(x$cache_path_get(), "foo.txt"))
```

## list the files

```{r}
x$list()
```

## details

```{r}
x$details()
```

## delete by file name

```{r}
x$delete("foo.txt")
x$list()
```
